---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Cloudera Machince Learning R Docker Image

Repo to provide a CML template to build images suitable to `R` users when:

+ No `sudo` access is provided on CML for users to install `ubuntu` libs.
+ Ensure `libudunits2-dev` is part of the ubuntu install.
+ You want minimize setup time for advanced users with the following libraries pre-installed:

```{r, echo=FALSE}

p <- sort(c("rmarkdown","bizdays","bookdown","learnr","caTools","corrr","corrplot","curl","RCurl","data.table","data.tree","devtools","doParallel","DiagrammeR","factoextra","rugarch","fGarch","fmsb","filesstrings","here","kableExtra","formatR","patchwork","gt","ggthemes","ggtext","gganimate","ggridges","scales","ggraph","igraph","gridtext","ggpubr","tufte","VennDiagram","desc","usethis","gifski","googleVis","googlesheets4","googledrive","flextable","Hmisc","caret","parsnip","glmnet","janitor","recipes","ranger","randomForest","anomalize","rpart.plot","htmltools","htmlwidgets","httr2","jsonlite","magrittr","vembedr","XML","webshot2","png","Cairo","widgetframe","magick","mongolite" ,"rhandsontable","shinycustomloader","wrapr","leaflet","tidygeocoder","rgdal","sp","lpSolve","lpSolveAPI","optimx","knitr","shiny","lubridate","moments","fitdistrplus","plotly","prettydoc","GGally","ggcorrplot","ggfortify","gganimate","prophet","e1071","naivebayes","splines2","revealjs","rstanarm","rjson","rvest","RSelenium","wdman","stringi","NLP","tidytext","textdata","lexicon","wordcloud2","robotstxt","tm","tm.plugin.webmining","widyr","riem","rlang","lobstr","sde","skimr","golem","shinipsum","slider","tidyquant","feasts","timetk","broom","broom.mixed","dials","infer","modeldata","modeldata","recipes","rsample","tune","workflows","workflowsets","yardstick","tint","tinytex","tufterhandout","pander","dplyr","tidyr","ggplot2","tibble","readr","purrr","stringr","forcats"))
p
```
# Building the image

In the same directory as the Dockerfile is:

```{r, eval=FALSE}
docker build "Dockerfile" -f docker:latest "."
```


